### 2021-06-21 src/paper/appendix_results.tex
Restructure for arxiv submission.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case_with_single_runs}
  \caption{Fit Over the Full Simulation Time Frame with Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported simulated infections rates. The mean infection rate is
  the thick blue line. Single simulation runs are plotted in lighter and thinner lines.
  The official case numbers as reported by the Robert-Koch-Institut are plotted in black.
  The fit is overall very good. The higher the mean incidence and the stronger the growth
  the more variance there is between simulation runs. We averaged over 30 simulation
  runs.}
  \label{fig:aggregated_fit2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_newly_infected_with_single_runs}
  \caption{Development of the Total Infections Over the Full Simulation Time Frame with
  Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the true weekly incidence rates
  per 100,000 people, including undetected cases. The mean infection rate is the thick
  blue line. Single simulation runs are plotted in lighter and thinner lines. The higher
  the mean incidence and the stronger the growth the more variance there is between
  simulation runs. We averaged over 30 simulation runs.}
  \label{fig:newly_infected_in_baseline}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Age Group}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported versus the simulated infections rates for different age
  groups. The age group of individuals above 80 needs to be interpreted with caution
  because our synthetic population only includes private households, i.e. nursing homes
  are not represented in our model. They accounted for many cases and deaths in the
  winter of 2020 and many 80 to 100 year olds live in these facilities. However, the
  official data does not contain information on whether cases were nursing home
  inhabitants or not. We averaged over 30 simulation runs.}
  \label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Federal State}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported versus the simulated infections rates for different
  federal states. We averaged over 30 simulation runs.}
  \label{fig:state_fit}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_ever_vaccinated}
  \caption{Share of Vaccinated Individuals}
  \floatfoot{\noindent \textit{Note:} The figure shows the rate of individuals that are
  vaccinated in our synthetic population versus in the general German population. Note
  that we excluded the vaccinations that were given to nursing homes, approximately the
  first percent of the German population that were vaccinated. Overall, our model covers
  a time frame that goes from zero vaccinated individuals to a state where over 40\% of
  the population are vaccinated. Our vaccinations work imperfectly but we do not model
  different vaccines nor do we distinguish between first and second shot.}
  \label{fig:fit_vaccinations}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_r_effective_with_single_runs}
  \caption{Effective Replication Number $R_t$ in the Model and as Reported by the
  Robert-Koch-Institute}
  \floatfoot{\noindent \textit{Note:} The figure shows the effective replication number
  ($R_t$) as reported by the RKI and as calculated in our model. The $R_t$ gives the
  average number of new infections caused by one infected individual. The $R_t$ in our
  model broadly follows the $R_t$ reported by the RKI. Two trends stand out. Firstly, the
  RKI's $R_t$ drops faster in November. This could be due to a change in the testing
  policy that focused tests on the elderly when the second wave hit Germany and led to a
  decline in the overall share of detected cases. The second difference is from mid
  February to mid March where the RKI's reported $R_t$ increased more rapidly than that
  in our model. Here the opposite effect can be expected. During this time rapid tests
  increased strongly leading to more cases being detected. In the short term this leads
  an $R_t$ estimation that is based on detected cases to overestimate the replication
  number.}
  \label{fig:fit_r_effective}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_share_b117_with_single_runs}
  \caption{Share of B.1.1.7 in the Model and as Reported by the Robert-Koch-Institute}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of B.1.1.7 as
  reported by the RKI and as calculated in our model. We only introduce a few cases over
  the cause of January. From then B.1.1.7 takes over endogenously through its increased
  infectiousness. We model no other features of B.1.1.7. At most we introduce 0.75 cases per 100,000 inhabitants.}
  \label{fig:fit_r_effective}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the
  \href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} for all of 2020 and
  then assume it to be constant as vaccinations of the elderly strongly affect the case
  fatality rate which the project does not account for. To get from an overall share of
  detected cases to the share of cases that is detected in each age group we use that
  asymptomatic cases are much less likely to be detected. As our model covers age
  specific asymptomatic rates this endogenously leads to group specific share known cases
  that verify that infections in younger age groups are under-detected. Starting in 2021
  in addition to the overall numbers of detected cases through symptoms and the share
  known cases, cases are also detected through confirmation of positive rapid tests. This
  leads to an increase in the share of known cases for all age groups but in particular
  for the younger age groups that are covered extensively with rapid tests through the
  rapid test requirement for participating in school.}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/educ_demand_share}
    \caption{Share of the Population Demanding a Rapid Test in an Education Setting}
    \label{fig:educ_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/work_demand_share}
    \caption{Share of the Population Demanding a Rapid Test due to Work}
    \label{fig:work_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/private_demand_share}
    \caption{Share of the Population Demanding a Rapid Test for Private Reasons}
  \label{fig:private_rapid_test_demand}
  \end{subfigure}
  \caption{Rapid Test Demand by Reason}
  \label{fig:rapid_test_demand_by_reason}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as school pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Tests are demanded by individuals for one of three private
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned weekly
    meeting with friends.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_educ_demand}
    \caption{Share of Rapid Tests in the Educational Setting Demanded by Infected
    Individuals}
    \label{fig:share_infected_among_educ_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_work_demand}
    \caption{Share of Work Rapid Tests Demanded by Infected Individuals}
    \label{fig:share_infected_among_work_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_private_demand}
    \caption{Share of Private Rapid Tests Demanded by Infected Individuals}
  \label{fig:share_infected_among_private_rapid_test_demand}
  \end{subfigure}
  \caption{Share of Rapid Tests Demanded by Infected Individuals by Reason}
  \label{fig:share_infected_among_rapid_test_demand_by_reason}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as school pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Tests are demanded by individuals for one of three private
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned weekly
    meeting with friends. Private rapid tests have a much higher share of infected
    individuals because they are mostly triggered by events that make an infection
    likely. Remember however, that one reason is that a household member has a positive
    rapid test. This means that work and education rapid tests which have a low rate of
    infected individuals trigger more targeted rapid tests through the household demand.
    They also have a much higher volume of tests. As can be seen in the decomposition
    (Figure~\ref{fig:2021_scenarios_decomposition_tests} every category of tests is
    important for the overall effect. It appears that the combination of wide testing to
    find infection chains plus targeted tests to break those chains taking together
    is important.}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
  \end{subfigure}%
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
  \end{subfigure}
  \caption{The Effect of Policies on Observed and Unobserved Cases}
  \label{fig:explain_decline}
  \floatfoot{\noindent \textit{Note:} \ldots}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case}
  \end{subfigure}%
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
  \end{subfigure}
  \caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
  \label{fig:school_scenarios_detailed}
\end{figure}

@@

\input{../figures/results/tables/student_infections_table}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case_with_single_runs}
  \caption{Fit Over the Full Simulation Time Frame with Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported simulated infections rates. The mean infection rate is
  the thick blue line. Single simulation runs are plotted in lighter and thinner lines.
  The official case numbers as reported by the Robert-Koch-Institut are plotted in black.
  The fit is overall very good. The higher the mean incidence and the stronger the growth
  the more variance there is between simulation runs. We averaged over 30 simulation
  runs.}
  \label{fig:aggregated_fit2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_newly_infected_with_single_runs}
  \caption{Development of the Total Infections Over the Full Simulation Time Frame with
  Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the true weekly incidence rates
  per 100,000 people, including undetected cases. The mean infection rate is the thick
  blue line. Single simulation runs are plotted in lighter and thinner lines. The higher
  the mean incidence and the stronger the growth the more variance there is between
  simulation runs. We averaged over 30 simulation runs.}
  \label{fig:newly_infected_in_baseline}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Age Group}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported versus the simulated infections rates for different age
  groups. The age group of individuals above 80 needs to be interpreted with caution
  because our synthetic population only includes private households, i.e. nursing homes
  are not represented in our model. They accounted for many cases and deaths in the
  winter of 2020 and many 80 to 100 year olds live in these facilities. However, the
  official data does not contain information on whether cases were nursing home
  inhabitants or not. We averaged over 30 simulation runs.}
  \label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Federal State}
  \floatfoot{\noindent \textit{Note:} The figure shows the weekly incidence rates per
  100,000 people for the reported versus the simulated infections rates for different
  federal states. We averaged over 30 simulation runs.}
  \label{fig:state_fit}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_ever_vaccinated}
  \caption{Share of Vaccinated Individuals}
  \floatfoot{\noindent \textit{Note:} The figure shows the rate of individuals that are
  vaccinated in our synthetic population versus in the general German population. Note
  that we excluded the vaccinations that were given to nursing homes, approximately the
  first percent of the German population that were vaccinated. Overall, our model covers
  a time frame that goes from zero vaccinated individuals to a state where over 40\% of
  the population are vaccinated. Our vaccinations work imperfectly but we do not model
  different vaccines nor do we distinguish between first and second shot.}
  \label{fig:fit_vaccinations}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_r_effective_with_single_runs}
  \caption{Effective Replication Number $R_t$ in the Model and as Reported by the
  Robert-Koch-Institute}
  \floatfoot{\noindent \textit{Note:} The figure shows the effective replication number
  ($R_t$) as reported by the RKI and as calculated in our model. The $R_t$ gives the
  average number of new infections caused by one infected individual. The $R_t$ in our
  model broadly follows the $R_t$ reported by the RKI. Two trends stand out. Firstly, the
  RKI's $R_t$ drops faster in November. This could be due to a change in the testing
  policy that focused tests on the elderly when the second wave hit Germany and led to a
  decline in the overall share of detected cases. The second difference is from mid
  February to mid March where the RKI's reported $R_t$ increased more rapidly than that
  in our model. Here the opposite effect can be expected. During this time rapid tests
  increased strongly leading to more cases being detected. In the short term this leads
  an $R_t$ estimation that is based on detected cases to overestimate the replication
  number.}
  \label{fig:fit_r_effective}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_b117_with_single_runs}
  \caption{Share of B.1.1.7 in the Model and as Reported by the Robert-Koch-Institute}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of B.1.1.7 as
  reported by the RKI and as calculated in our model. We only introduce a few cases over
  the cause of January. From then B.1.1.7 takes over endogenously through its increased
  infectiousness. We model no other features of B.1.1.7. At most we introduce 0.75 cases per 100,000 inhabitants.}
  \label{fig:fit_share_b117}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the
  \href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} for all of 2020 and
  then assume it to be constant as vaccinations of the elderly strongly affect the case
  fatality rate which the project does not account for. To get from an overall share of
  detected cases to the share of cases that is detected in each age group we use that
  asymptomatic cases are much less likely to be detected. As our model covers age
  specific asymptomatic rates this endogenously leads to group specific share known cases
  that verify that infections in younger age groups are under-detected. Starting in 2021
  in addition to the overall numbers of detected cases through symptoms and the share
  known cases, cases are also detected through confirmation of positive rapid tests. This
  leads to an increase in the share of known cases for all age groups but in particular
  for the younger age groups that are covered extensively with rapid tests through the
  rapid test requirement for participating in school.}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/educ_demand_share}
    \caption{Share of the Population Demanding a Rapid Test in an Education Setting}
    \label{fig:educ_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/work_demand_share}
    \caption{Share of the Population Demanding a Rapid Test due to Work}
    \label{fig:work_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/private_demand_share}
    \caption{Share of the Population Demanding a Rapid Test for Private Reasons}
  \label{fig:private_rapid_test_demand}
  \end{subfigure}
  \caption{Rapid Test Demand by Reason}
  \label{fig:rapid_test_demand_by_reason}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as school pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Tests are demanded by individuals for one of three private
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned weekly
    meeting with friends.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/share_infected_among_educ_demand}
    \caption{Share of Rapid Tests in the Educational Setting Demanded by Infected
    Individuals}
    \label{fig:share_infected_among_educ_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/share_infected_among_work_demand}
    \caption{Share of Work Rapid Tests Demanded by Infected Individuals}
    \label{fig:share_infected_among_work_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/share_infected_among_private_demand}
    \caption{Share of Private Rapid Tests Demanded by Infected Individuals}
  \label{fig:share_infected_among_private_rapid_test_demand}
  \end{subfigure}
  \caption{Share of Rapid Tests Demanded by Infected Individuals by Reason}
  \label{fig:share_infected_among_rapid_test_demand_by_reason}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as school pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Tests are demanded by individuals for one of three private
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned weekly
    meeting with friends. Private rapid tests have a much higher share of infected
    individuals because they are mostly triggered by events that make an infection
    likely. Remember however, that one reason is that a household member has a positive
    rapid test. This means that work and education rapid tests which have a low rate of
    infected individuals trigger more targeted rapid tests through the household demand.
    They also have a much higher volume of tests. As can be seen in the decomposition
    (Figure~\ref{fig:2021_scenarios_decomposition_tests} every category of tests is
    important for the overall effect. It appears that the combination of wide testing to
    find infection chains plus targeted tests to break those chains taking together
    is important.}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
  \end{subfigure}%
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
  \end{subfigure}
  \caption{The Effect of Policies on Observed and Unobserved Cases}
  \label{fig:explain_decline}
  \floatfoot{\noindent \textit{Note:} \ldots}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case}
  \end{subfigure}%
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
  \end{subfigure}
  \caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
  \label{fig:school_scenarios_detailed}
\end{figure}

@@

\input{figures/results/tables/student_infections_table}

### 2021-06-21 src/paper/model/course_of_disease.tex
Restructure for arxiv submission.

The following medical parameters describing the progression of the disease are taken from
systematic reviews (e.g. \citet{He2020}). After an infection occurs, the disease
progresses in the way depicted in Figure~\ref{fig:model_disease_progression}.

First, infected individuals will become infectious after one to five days. About one
third of people remain asymptomatic. The rest develop symptoms about one to two days
after they become infectious. Modeling asymptomatic and pre-symptomatic cases is
important because those people do not reduce their contacts or demand a test and can
potentially infect many other people \citep{Donsimoni2020}. The probability to develop
symptoms with Covid-19 is highly age dependent with 75\% of children not developing
symptoms \citep{Davies2020}.

@@

We allow the progression of the disease to be stochastic in two ways: Firstly, state
changes only occur with a certain probability (e.g. only a fraction of infected
individuals develops symptoms). Secondly, the number of periods for which an individual
remains in a state is drawn randomly. The parameters that govern these processes are
taken from the literature \footnote{ Detailed information on the calibration of the
disease parameters is available as part of our
\href{https://sid-dev.readthedocs.io/en/latest/reference_guides/epi_params.html}{online
documentation}.} and age-dependent.

>>>>

The disease progression in the model is fairly standard. It is depicted in
Figure~\ref{fig:model_disease_progression} and the values and source of the relevant
parameters are describes in Section~\ref{sec:medical_params}.

First, infected individuals will become infectious after one to five days. Overall,
about one third of people remain asymptomatic. The rest develop symptoms about one to
two days after they become infectious. Modeling asymptomatic and pre-symptomatic cases
is important because those people do not reduce their contacts nor do they have an
elevated probability to demand a test. Thus they can potentially infect many other
people \citep{Donsimoni2020}. The probability to develop
symptoms with Covid-19 is highly age dependent with 75\% of children not developing
clinical symptoms \citep{Davies2020}.

@@

We allow the progression of the disease to be stochastic in two ways: Firstly, state
changes only occur with a certain probability (e.g. only a fraction of infected
individuals develops symptoms). Secondly, the number of periods for which an individual
remains in a state is drawn randomly. The parameters that govern these processes are
taken from the literature \footnote{ Detailed information on the calibration of the
disease parameters is available as part of our
\href{https://sid-dev.readthedocs.io/en/latest/reference_guides/epi_params.html}{online
documentation}.}.\comment[id=J]{Replace this by a link to the relevant table with
parameters in the data appendix, once we have that table.}

### 2021-06-21 src/paper/model/estimated_parameters.tex
Restructure for arxiv submission.

We estimate parameters that cannot be calibrated outside of the model with the
method of simulated moments \citep{McFadden1989} by minimizing the distance between
simulated and observed infection rates. Since our model includes a lot of randomness, we
average simulated infection rates over several model runs.

>>>>

We estimate parameters that cannot be calibrated outside of the model with the
method of simulated moments \citep{McFadden1989} by minimizing the distance between
simulated and observed infection rates and fatality rates (disaggregated by region
and age groups). Since our model includes a lot of randomness, we
average simulated infection rates over several model runs.

### 2021-06-21 src/paper/model/number_of_contacts.tex
Restructure for arxiv submission.

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only
those 50 people had contact with an infectious person and the disease has an infection
probability of 1 in each contact or whether everyone met an infectious person but the
disease has an infection probability of only 5 percent per contact. SEIR models do not
distinguish contact frequency from the infectiousness of each contact and
combine the two in one parameter that is not invariant to social distancing policies.

@@

In our empirical application we distinguish the following types of contacts:\comment[id=HM]{I started updating this to understand it better myself. In the end, I think it will be useful to group into HH / work / schools and add an introductory sentence for each group. E.g., that work is for everybody who is working --- except there is a different model for teachers (?), ...}

@@

    \item Recurrent daily non-work contacts representing very close family or friendship
    relations outside the household.

    \item Recurrent weekly non-work contacts representing friendships, sports groups,
    charity work, or other activities. We randomize over the days on which the meetings take place.\comment[id=HM]{True?}

    \item Random non-work contacts: Contacts with randomly drawn other
    people, which are assortative with respect to region and age group. This contact type
    reflects contacts during leisure activities, grocery shopping, medical appointments,
    etc..

    \item Recurrent daily work contacts, capturing direct colleagues.

    \item Recurrent weekly work contacts, representing meetings with clients, superiors, or more distant colleagues.
    We randomize over the days on which the meetings take place.

    \item Random work contacts: Working adults' contacts with randomly drawn other
    people, which are assortative in geographical location\comment[id=HM]{True? age?}

    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age. Schools
    are closed on weekends and during vacations, which vary by states. School classes
    also meet three pairs of teachers every school day. The pairs are meant to represent
    interactions between teachers.\comment[id=HM]{Not updated from here on. Mayb}

@@

    \item Nurseries: Children younger than three years may attend a nursery and interact
    with one adult. The age of the children varies within groups. The remaining
    mechanics are similar to schools.
\end{itemize}

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{sec:number_of_contacts}. In particular, we sample the number of contacts or
group sizes from empirical distributions that sometimes depend on age. It is also
possible to use economic or other behavioral models to predict the number of contacts.

Theoretically, each contact type can have its own infection probability. However, to
reduce the number of free parameters and thus avoid a potential over-fitting we only
estimate different infection probabilities for the areas work, school, preschool and
nurseries, households and other contacts.

>>>>

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only
those 50 people had contact with an infectious person and the disease has an infection
probability of 1 per contact or whether everyone met an infectious person but the
disease has an infection probability of only 5 percent per contact. SEIR models do not
distinguish contact frequency from the infectiousness of each contact and
combine the two in one parameter that is not invariant to social distancing policies.

@@

In our empirical application we distinguish the following  contact types that
are depicted in Figure~\ref{fig:model_contacts_infections} and can be further grouped
in the categories household, work, education and others.

types of contacts:\comment[id=HM]{I started updating this to understand it better myself. In the end, I think it will be useful to group into HH / work / schools and add an introductory sentence for each group. E.g., that work is for everybody who is working --- except there is a different model for teachers (?), ...}

@@

    \item Recurrent work contacts, capturing contacts with coworkers, repeating
          clients and superiors. Some of these recurrent contacts take place on
          every workday, others just once per week.

    \item Random work contacts: Working adults have contacts with randomly drawn other
          people, which are assortative in geographical location and age.

    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age. Schools
    are closed on weekends and during vacations, which vary by states. School classes
    also meet six teachers everyday and some of the teachers meet each other.

@@

    \item Nurseries: Children younger than three years may attend a nursery and interact
    with one adult. The age of the children varies within groups. The remaining
    mechanics are similar to schools.

    \item Random other contacts: Contacts with randomly drawn other
    people, which are assortative with respect to geographic location and and age group.
    This contact type reflects contacts during leisure activities, grocery shopping,
    medical appointments, etc..

    \item Recurrent other contacts representing contacts with friends neighbors or
        family members who do not live in the same household. Some of these contacts
        happen daily, others only once per week.

\end{itemize}

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{sec:number_of_contacts}. In particular, we sample the number of contacts or
group sizes from empirical distributions that sometimes depend on age. It would also be
possible to use economic or other behavioral models to predict the number of contacts.

% Theoretically, each contact type can have its own infection probability. However, to
reduce the number of free parameters and thus avoid a potential over-fitting we only
estimate different infection probabilities for the areas work, school, preschool and
nurseries, households and other contacts.

### 2021-06-21 src/paper/model/summary.tex
Restructure for arxiv submission.

The structure of the model is depicted in Figure~\ref{fig:model_contacts_infections}.
\comment[id=HM]{Mentioned by Tim in the course, just main paper: Modular structure may deserve a sentence}

The background characteristics include age, county and occupation of each simulated
individual. Contact models are functions that map individual characteristics into a
predicted number of contacts. Currently, we distinguish between eight types of contact
models which are all listed in Figure~\ref{fig:model_contacts_infections}: households,
recurrent and random work contacts, recurrent and random leisure contacts, and nursery,
preschool, and school contacts.

The predicted number of contacts is translated into infections by a matching algorithm.
There are different matching algorithms for recurrent contacts (e.g. classmates, family
members) and non-recurrent contacts (e.g. clients, contacts in supermarkets). The
infection probability can differ for each contact type. All types of contacts can be
assortative with respect to geographic and demographic characteristics.

@@

Another key advantage of the model is that the number of contacts an individual has of
each contact type can be calibrated from publicly available data \citep{Mossong2008}.
This in turn allows us to estimate policy-invariant infection probabilities from time
series of infection and death rates using the method of simulated moments
\citep{McFadden1989}. Since the infection probabilities are time-invariant, data
collected since the beginning of the pandemic can be used for estimation. Moreover,
since we model the testing strategies that were in place at each point in time, we can
correct the estimates for the fact that not all infections are observed.

Last but not least, performing simulations whose starting point is set amidst the
pandemic requires special adjustments to arrive at a realistic distribution of courses
of diseases. We solve the initial conditions problem by matching reported infections to
individuals in our data while also correcting for reporting lag and undetected cases.

In the following sections we describe each of the model components in more detail.

>>>>

The structure of the model is depicted in Figure~\ref{fig:model_contacts_infections}.

We distinguish between eight types of contact
models which are all listed in Figure~\ref{fig:model_contacts_infections}: households,
recurrent and random work contacts, recurrent and random leisure contacts, and nursery,
preschool, and school contacts.

The number of contacts is translated into infections by a matching algorithm.
There are different matching algorithms for recurrent contacts (e.g. classmates, family
members) and non-recurrent contacts (e.g. clients, contacts in supermarkets).
All types of contacts can be assortative with respect to geographic and demographic
characteristics.

@@

An important feature of the model is that the number of contacts an individual has of
each contact type can be calibrated from publicly available data \citep{Mossong2008}.
This in turn allows us to estimate policy-invariant infection probabilities from time
series of infection and death rates using the method of simulated moments
\citep{McFadden1989}. Since the infection probabilities are time-invariant, data
collected since the beginning of the pandemic can be used for estimation. Moreover,
since we model the testing strategies that were in place at each point in time, we can
correct the estimates for the fact that not all infections are observed.

The model has a very modular structure and can easily be extended to distinguish more
contact types, add more stages to the disease progression, implement new policies
or test demand models. The main bottleneck is not complexity or computational cost
but the availability of data to calibrate the additional model features.
